### 2024-08-03 conteudo/apendices/emp-lista.tex
create appendix

THIS APPENDIX IS FOR LIST THE RANDOM SELECTED FUNCTIONS PAIRS IN THE 
EMPIRICIAL ANALYSES OF THE TOOL. I will put it here later.

>>>>

\label{app:emp}

This appendix includes the list of function pairs used to evaluate the tool, as 
described in section \ref{sec:metemp}. 
The results are available in Table \ref{tab:emp}. 
The files indicate the relative path to the AMD Display driver root directory.

\input{conteudo/apendices/cem}

\input{conteudo/apendices/noventa}

\input{conteudo/apendices/oitenta}

\input{conteudo/apendices/setenta}

\input{conteudo/apendices/sesenta}

\input{conteudo/apendices/cinquenta}

\input{conteudo/apendices/quarenta}

\input{conteudo/apendices/trinta}

### 2024-08-03 conteudo/methods/methods.tex
add initial preliminar
add refer to repository
create appendix

To make the random selection of function pairs, we list the code duplications for each of the 
X variations and execute a random selection algorithm built into the source code language of 
our tool. The random selected function selected function pairs can 
be found in the Appendix (CREATE Appendix AND ADD HERE).

@@

@@

Finishing our mitigation method, if the mitigation ends up working in an initial step, we may 
move it forward to the Ethnographic method, interacting with the Linux community to understand 
their thoughts on the mitigation. If the mitigation ends up not working as expected, we will 
categorize it in two categories, the first one is that the refactoring requires a decision in 
which we, as not specialists and non-maintainers of the Linux kernel, cannot make it correctly,
although we believe a specialist would be able to refactor it. The second categorization is 
that we do not know if it is possible to refactor the duplication. With or without successful 
mitigation, we will store our mitigations on (ADD REP AND PUT HERE) to research transparency.

>>>>

To make the random selection of function pairs, we list the code duplications for each of the 
X variations and execute a random selection algorithm built into the source code language of 
our tool. The random selected function selected function pairs can 
be found in the Appendix \ref{app:emp}.

@@

\label{sec:meteth}

@@

Finishing our mitigation method, if the mitigation ends up working in an initial step, we may 
move it forward to the Ethnographic method, interacting with the Linux community to understand 
their thoughts on the mitigation. If the mitigation ends up not working as expected, we will 
categorize it in two categories, the first one is that the refactoring requires a decision in 
which we, as not specialists and non-maintainers of the Linux kernel, cannot make it correctly,
although we believe a specialist would be able to refactor it. The second categorization is 
that we do not know if it is possible to refactor the duplication. With or without successful 
mitigation, we will store our mitigations on \url{https://github.com/LipArcanjo/master-artifacts} 
to research transparency.
